### 2018-07-31 other_R_code/article_selection_process.Rnw
Further development of classification write-up

\section{The data}
<<loaddata, cache=TRUE, tidy=TRUE>>=
classdocs<-durhamevp::get_classified_docs()
classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)
@

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}
<<findkeywords>>=
keywords<-nb_keywords(classified_dfm, "EV_article")
knitr::kable(head(keywords, 20))
@

@@

nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()
@

@@

@@

\subsection{Partition $S$ into $T$ and $S \backslash T$}

\subsection{Discovering Keywords to Classify Documents}

\subsection{Human Input and Human-Computer Iteration}
\end{document}

>>>>

\section{The data}
<<loaddata, cache=TRUE, tidy=TRUE>>=
classdocs<-durhamevp::get_classified_docs()
# just some candidate document for speed/space reasons
unclassdocs<-durhamevp::get_candidate_documents(3000:6000)

@

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}
<<findkeywords>>=
classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)

keywords<-nb_keywords(classified_dfm, "EV_article")
knitr::kable(head(keywords, 20))
@

@@

nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()

description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

@

@@

\subsection{More realistic use case}
Exclude non-election cases which would not be returned by our keywords:

<<usingdescriptionrealistic, warning=FALSE>>=
description_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,c("fakeid", "description", "EV_article")], text_field = "description")
description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()

description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

@

@@

\subsection{Partition $S$ into $T$ and $S \backslash T$}
To partition $S$ into $T$ and $S \backslash T$, we first define a `training' set by sampling from $S$ and $R$. Since $R$ is typically much smaller than $S$ our test set for our classifiers is all all of $S$, we often use the entire $R$ set and a sample of $S$ as our training set.
<<fitkingtrain>>=
R <- classdocs[classdocs$EV_article==1,]
R$R <- 1
R$in_sample<-1
S <- unclassdocs
S$R <- 0

n_sample_S <- 1000
S$in_sample<-0
S$in_sample[sample(1:nrow(S), n_sample_S)]<-1

R_S <- dplyr::bind_rows(R, S)
R_S$fakeid<-1:nrow(R_S)

R_S_corpus<-quanteda::corpus(R_S[,c("fakeid", "ocr", "in_sample", "R")], text_field = "ocr")
R_S_dfm <- preprocess_corpus(R_S_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 20)

king_train_dfm<-quanteda::dfm_subset(R_S_dfm, quanteda::docvars(R_S_dfm, "in_sample")==1)
king_nb <- quanteda::textmodel_nb(king_train_dfm, y=quanteda::docvars(king_train_dfm, "R"), prior="uniform")
keywords<-nb_keywords(king_train_dfm, "R")
knitr::kable(head(keywords, 20))
@

After fitting the classifiers, we use the estimated parameters to generate predicted probabilities of $R$ membership for all documents in $S$. Of cource, all the search set documents in fact fall within $S$ but our interest in in learning from the \textit{mistakes} these classifiers make.

<<learnclassmistakes>>=
S_dfm <- quanteda::dfm_subset(R_S_dfm, quanteda::docvars(R_S_dfm, "R")==0)
quanteda::docvars(S_dfm, "T")<-predict(king_nb, newdata = S_dfm, type="class")
@

\subsection{Discovering Keywords to Classify Documents}
After partitioning $S$ into estimated target $T$ and non-target set $S \backslash T$, we must find and rank keywords which best discriminate $T$ and $S \backslash T$.
King does this in three stages:
\subsubsection{identify keywords in S}

\subsubsection{sort them into those that predict each of the two steps}

My suggestion here is simply to use binary\_dfm

<<>>=
S_dfm_binary<-quanteda::dfm_weight(S_dfm, scheme="boolean")
king_stage2 <- quanteda::textmodel_nb(S_dfm, y=quanteda::docvars(S_dfm_binary, "T"), distribution="Bernoulli")
king_stage2 <- nb_keywords(S_dfm, "T")
knitr::kable(head(king_stage2, 30))

knitr::kable(tail(king_stage2, 30))
@

\subsection{rank them by degree of discriminatory power}
We already seem to have done this in the step above
\subsection{Human Input and Human-Computer Iteration}
Now present

\end{document}
